Title

### 2020-05-02 Final Draft.Rmd
table 1 formatting

---
title: "Investigating the Underprovision of Public Goods: Does Segregation Matter?"
author: "Maria Burzillo"
date: "5/8/2020"
output: 
  pdf_document:
    fig_caption: true
bibliography: final_proj_bib.bib
#biblio-style: "apalike"
link_citations: true
header_includes: \usepackage{float}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(gtable)
library(stargazer)
library(tidyverse)
library(gt)
library(gtsummary)
library(knitr)
library(lme4)
library(margins)
library(reprex)
library(plm)
library(devtools)
library(lfe)
library(Statamarkdown)
library(readxl)
library(starpolishr)
library(AER)
library(readxl)
library(naniar)
library(mice)
library(gtsummary)
library(VIM)
library(kableExtra)
```

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"), srt = 45)
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1, srt = 45)
# this plot tells us that only .58% of the data are complete (not missing anything)

@@

```{r results="asis", echo = FALSE, fig.cap= "THIS IS A CAPTION IS IT WORKING WHAT IS GOING ON!"}

@@

t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
                header = FALSE,
                title = "\\textbf{Racial Polarization in Segregated Cities}",
                single.row = TRUE,
                no.space = FALSE,
                keep.stat = c("n"),
                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
                dep.var.labels = c("Racial Divide"),
                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
                notes = "This table displays the results of the replication\neffort of the analyses conducted in Trounstine (2016) using the racial polarization dataset.\nThe replication code can be found on my personal Github repository, which is linked in the introduction. The original table is displayed for comparison as Figure 1.)",
                table.placement = "H",
                notes.align = "l")

# note: "This table displays the results of the replication effort of the analyses conducted in Trounstine (2016) using the racial polarization dataset. The replication code can be found on my personal [Github repository](https://github.com/mburzillo/new_final_project). The original table is displayed for comparison as Figure 1.")

>>>>

---
title: "Investigating the Underprovision of Public Goods: Does Segregation Matter?"
author: "Maria Burzillo"
date: "5/8/2020"
output: 
  pdf_document:
    fig_caption: true
bibliography: final_proj_bib.bib
#biblio-style: "apalike"
link_citations: true
header_includes: 
  \usepackage{float}
  \usepackage{multirow}

@@

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)
library(haven)
library(stargazer)
library(tidyverse)
library(gtsummary)
library(knitr)
library(AER)
library(lme4)
library(margins)
library(lfe)
library(readxl)
library(mice)
library(VIM)
library(kableExtra)
```

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)
# this plot tells us that only .58% of the data are complete (not missing anything)

@@

```{r results="asis", echo = FALSE}

@@

t1 <- stargazer(m1, m2, m3, omit = c("year", "south", "midwest", "west"),
                header = FALSE,
                style = "apsr",
                title = "\\textbf{Racial Polarization in Segregated Cities}",
                single.row = FALSE,
                no.space = F,
                keep.stat = c("n"),
                covariate.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Diversity", "Percent Asian", "Percent Black", "Percent Latino", "Medain HH Income (1000s)", "Percent Renters", "Percent College Degree", "Biracial Contest", "Nonpartisan Election", "Primary Election", "Population (logged)", "White Ideology", "Constant"),
                dep.var.labels = c("\\textbf{\\underline{Racial Divide with:    }}"),
                column.labels = c("Multigroup H Index", "White/Nonwhite H Index", "Ideology Controls"),
                notes = c("Table 1: This table displays the results of the replication effort of the analyses conducted in Trounstine (2016)", 
                          "using the racial polarization dataset. The replication code can be found on my personal Github repository, which is",
                          " linked in the introduction. The original table is displayed for comparison as Figure 3."),
                table.placement = "H",
                notes.align = "l",
                #column.sep.width = "-10pt",
                font.size = "small")

#c("\\textbf{Table 1:} This table displays the results of the replication effort",
#                          "of the analyses conducted in Trounstine (2016) using the racial",
#                          "polarization dataset. The replication code can be found on my
#                          personal", "Github repository, which is linked in the introduction.",
#                          "The original table is displayed for comparison as Figure 3.")

### 2020-05-02 stargazer_reprex.Rmd
table 1 formatting

---
title: "Title"
author: "Author"
output: 
  pdf_document:
    fig_caption: yes
    extra_dependencies: ["rotating"]
header_includes:
  \usepackage{float}
  \usepackage{dcolumn}
  \usepackage{rotating}
  \restylefloat{table}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.position = "!H")
library(tidyverse)
library(stargazer)
library(reprex)
```

```{r results = "asis", echo = FALSE}

@@

t1 <- stargazer(output, output2, 
                header = FALSE,
                title = "\\textbf{Practice Table}",
                notes = "Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. Notes Could Go Here???????????? This is an example. ",
                notes.align = "l",
                float = FALSE,
                table.placement = "H")

@@

>>>>

---
title: "Title"
author: "Author"
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    extra_dependencies: ["rotating"]
header_includes:
  \usepackage{float}
  \usepackage{dcolumn}
  \usepackage{rotating}
  \restylefloat{table}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.position = "!H")
library(tidyverse)
library(stargazer)
library(reprex)
library(kableExtra)
library(huxtable)
```

# Simple Plot

```{r fig.cap= "this is a caption", echo = FALSE}
mtcars %>%
  ggplot(aes(x = disp, y = mpg )) +
  geom_point()

# Stargazer

```{r results = "asis", echo = FALSE, fig.cap= "this is my captions"}

@@

t1 <- stargazer(output, output2, 
                header = FALSE,
                title = "\\textbf{Practice Table}",
                notes = c("Notes Could Go Here????????????", "This is an example. Notes Could Go Here???????????? This is an example.", "Notes Could Go Here???????????? This is an example.", "Notes Could Go Here???????????? This is an example. "),
                notes.align = "l",
                notes.append = F,
                float = FALSE,
                style = "apsr",
                table.placement = "H")

@@

```{r fig.cap="this is my caption", echo = FALSE, warning=FALSE}
huxreg(output, output2)
```
